---
title: "Assignment Two for Lab 2"
author: "Taehoon Ha"
date: "09/23/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### 1. Read Chapters 3, 5, 12, 13 from "R for data science" (online version).

### 2. Create a GitHub repository Lab2 (files with R code for this assignment should be added to this repository, do not push csv files for Problem 4 to the GitHub repo).

### 3. Write the R code to recreate the graph from the Activity 2 (Problem 4).
#### 3.1 Downlad lab2.csv file:
  * time: base, first, second
  * category: sport (sport activity), qol (quality of life), pain
```{r}
library(tidyverse)
library(ggplot2)

lab2 <- read.csv('lab2.csv')
```

#### 3.2 Make the data tidy.
```{r}
df <- lab2 %>%
  gather(key = time_category, value = case, indexes = 2:10) %>%
  separate(time_category, into = c("time", "category"), sep = "_") %>%
  mutate(new.time = recode(time, 'base' = 'baseline',
                'first' = 'one year',
                'second' = 'two years')) %>%
  select(patient_id, new.time, category, case)

```

#### 3.3 Summarize by time and category (mean and standard deviation)
```{r}
df <- df %>% 
  group_by(new.time, category) %>%
  summarise(Mean = round(mean(case), 2), SD = round(sd(case), 2))

df
```

#### 3.4 Write the R code to recreate the following graph (please note that tick mark labels are changed):
```{r}
pd <- position_dodge(.2)

ggplot(df, aes(x = new.time, y = Mean, group = category, color = category)) +
  geom_point(position = pd) +
  geom_line(position = pd) +
  geom_errorbar(aes(ymin = df$Mean - df$SD, ymax = df$Mean + df$SD), width = 0.1, size = 1, position = pd ) +
  theme_bw() +
  labs(x = "Time of report", y = "Sample mean and standard deviation") +
  ylim(0, 100) +
  theme(legend.position = c(0.9, 0.2), legend.title = element_blank())
```

### 4. Download two files:
  * **coverage.csv** - Health Insurance Coverage of the Total Population (2013 - 2016)
  * **expenditures.csv** - Health Care Expenditures by State of Residence (in millions)
```{r}
coverage <- read.csv('coverage.csv', skip = 2, nrows = 52, header = T, sep = ',', stringsAsFactors = F)

expenditures <- read.csv('expenditures.csv', skip = 2, nrows = 52, header = T, sep = ',', stringsAsFactors = F)
```

#### 4.1 Make the data frames "tidy."
```{r}
tidy.coverage <- coverage %>% 
  gather(key = XYear__InsType, value = Total.Covered, indexes = 2:ncol(coverage)) %>%
  separate(XYear__InsType, into = c("XYear", "InsType"), sep = '__') %>%
  mutate(Year = gsub("X","", XYear)) %>%
  select(Location, Year, InsType, Total.Covered)

tidy.coverage %>% head

tidy.expenditures <- expenditures %>% 
  gather(XYear__Total.Health.Spending, value = Total.Spent, indexes = 2:ncol(expenditures)) %>%
  separate(XYear__Total.Health.Spending, into = c("XYear", "Category"), sep = '__') %>%
  mutate(Year = gsub("X","", XYear)) %>%
  select(Location, Year, Total.Spent)

tidy.expenditures %>% head
```

#### 4.2 Merge two data frames: the resulting data frame should contain information about coverage and expenditures for years 2013-2016. Please note that file **expenditures.csv** does not contain years 2015-2016.
```{r}
merge(tidy.coverage, tidy.expenditures, by = c("Location", "Year"), all = T) %>%
  filter(Year >= 2013 & Year <= 2016)
```

### 5. Submit a link to the repo “Lab2” via Canvas.
